Reproducible Research: Peer Assessment 1
-----------------------------------------

### Loading and preprocessing the data

```{r}
rm(list=ls())
data<- read.csv("activity.csv", colClasses = c("numeric", "Date", "numeric"))
Sys.setlocale("LC_TIME", "C")
head(data, 3)
```

### What is mean total number of steps taken per day?

**Make a histogram of the total number of steps taken each day**

```{r figure1}
datasum<- aggregate(steps~date, data = data, sum, na.rm = T)
hist(datasum$steps, col = 5,
     main = "Total steps taken per day",
     xlab = "Steps")
rug(datasum$steps)
```

### Calculate and report the mean and median total number of steps taken per day

**Mean**
```{r}
mean(datasum$steps) 
```

**Median**
```{r}
median(datasum$steps)
```

### Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r plot2}
library(ggplot2)
z<- aggregate(steps~interval, data = data, mean)
qplot(interval, steps, data = z, geom = "line")
```

### Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
which.max(z$steps)
z$interval[which.max(z$steps)]
```

###Imputing missing values

**Calculate and report the total number of missing values in the dataset**
```{r}
sum(is.na(data$steps))

```

###Devise a strategy for filling in all of the missing values in the dataset

**I replace NA`s whith the mean value of steps**
```{r}
dataNa<- data
dataNa[is.na(dataNa)] <- mean(dataNa$steps, na.rm=TRUE)
head(dataNa)
```
Create a new dataset that is equal to the original dataset but with the
missing data filled in.
```{r}
str(dataNa)
``` 

**Make a histogram of the total number of steps taken each day and Calculate**
**and report the mean and median total number of steps taken per day.**
```{r}
dataNaz<- aggregate(steps~date, data = dataNa, sum)
ggplot(dataNaz, aes(x = steps)) + 
        geom_histogram(fill = "green", colour = "black") +
        geom_vline(xintercept = mean(dataNaz$steps),
                   color = "red", linetype = "dashed", size = 1)

```

**Total number of steps taken per day.**

```{r}
mean(dataNaz$steps)
median(dataNaz$steps)
```

### Are there differences in activity patterns between weekdays and weekends?

Create a new factor variable in the dataset with two levels – “weekday”
and “weekend” indicating whether a given date is a weekday or weekend
day.
```{r}
dataNazWeekend<- as.factor(ifelse(weekdays(dataNaz$date) %in% c("Saturday", "Sunday"), "Weekday", "Weekends"))
a<- cbind(dataNa, dataNazWeekend)
```

Make a panel plot containing a time series plot (i.e. type = "l") of the
5-minute interval (x-axis) and the average number of steps taken, averaged
across all weekday days or weekend days (y-axis).

```{r}
ggplot(a, aes(x = interval, y = steps)) + 
        geom_bar(stat = "identity") + 
        facet_grid(. ~dataNazWeekend)
```



